---
title: "P8105_HW1_JG4890"
output: github_document
date: "2024-09-21"
---
## Question 1
## Import Data
```{r}
data("penguins", package = "palmerpenguins")
library(dplyr)
library(ggplot2)
```

## Data set description
```{r}
n_rows <- nrow(penguins)
n_cols <- ncol(penguins)
mean_flipper_length <- mean(penguins$flipper_length_mm, na.rm = TRUE)
```
This dataset has 8 cols and 344 rows in total.The columns contains 8 different variables which are species, island, bill length, bill depth, flipper length, body mass, sex and year.

species: 3 species of penguins - Adelie, Gentoo, Chinstrap

island: 3 islands of observed - Torgersen, Biscoe, Dream

bill length mm: Range from 32.1 to 59.6

bill depth mm: Range from 13.1 to 21.5

flipper length mm: Range from 172 to 231

body mass g: Range from 2700 to 6300

sex: Male or Female

year: From 2007 to 2009

The mean flipper length is 200.92 mm.

## Scatterplot
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Flipper Length vs Bill Length", x = "Bill Length (mm)", y = "Flipper Length (mm)") +
  theme_minimal()

ggsave("scatterplot_penguins.png")
```
The scatter plot visualizes the relationship between flipper length(Y-axis) and bill length(X-axis) for different penguin species, with all three species represented in different colors. The graph shows clear differences in these measurements across species. There was some missing information when the scatterplot was saved, so 2 rows with missing values were removed from the dataset before drawing. This ensures that only the complete data points are displayed in the scatter plot.

##Question 2

## Create a data frame
```{r}
library(tidyverse)
set.seed(1)
sample_normal <- rnorm(10)
logical_vector <- sample_normal > 0
character_vector <- LETTERS[1:10]
factor_vector <- factor(sample(c("Low", "Medium", "High"), 10, replace = TRUE))

df <- data.frame(
  normal_sample = sample_normal,
  logical_greater_than_0 = logical_vector,
  character = character_vector,
  factor = factor_vector
)
print(df)
```

## Calculate the means
```{r}
mean_normal <- mean(pull(df, normal_sample))
mean_logical <- mean(pull(df, logical_greater_than_0))
mean_character <- mean(pull(df, character))  
mean_factor <- mean(pull(df, factor))        
```
Mean of normal_sample works because it’s numeric.

Mean of logical_greater_than_0 works because logical values are coerced to numeric (TRUE becomes 1 and FALSE becomes 0).

Mean of character produces an error because character data cannot be coerced to numeric directly.

Mean of factor also produces an error because factors must be converted to numeric properly (they represent levels, not direct values).

## Convert variables
```{r}
numeric_logical <- as.numeric(df$logical_greater_than_zero)
numeric_character <- as.numeric(df$character)  
numeric_factor <- as.numeric(df$factor)     

#print(numeric_logical)
#print(numeric_character)
#print(numeric_factor)
```
Logical to Numeric: Converts TRUE to 1 and FALSE to 0.

Character to Numeric: Produces NA for all values since character strings cannot be converted to numbers.

Factor to Numeric: Converts to the underlying integer codes for the factor levels (not the actual levels itself).

Converting variables reveals how R interprets and handles different data types during calculations, so it helps explain what happens when you try to take the mean.
